\documentclass{resume} % Use the custom resume.cls style
\usepackage{hyperref}
\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Arihant Chawla} % Your name
\address{3063 Sector 38D, Chandigarh} 
\address{(+91)9501580708 \\ arihantchawla.becse17@pec.edu.in} % Your phone number and email

\begin{document}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

{\bf Punjab Engineering College, Chandigarh \hfill {\em2017-Present}} 
\\ B.E. Computer Science
\hfill GPA: \emph{8.43/10} 
\\ Relevant courses: Design and Analysis of Algorithms, Data Structures, Digital Electronics and Logic Design, Discrete Mathematics, Vector Calculus
\\ \\{\bf DAV Model School, Chandigarh \hfill {\em2015-2017}}\\
CBSE, All India Senior School Certificate Examination \hfill \emph{90.2\%}
\\ \\{\bf Sacred Heart Sr. Sec. School, Ludhiana \hfill {\em2005-2015}}\\
CBSE, All India Secondary School Examination \hfill \emph{GPA 10}
\end{rSection}

\begin{rSection}{Internships and Volunteer Experience}

\begin{rSubsection}{Code57, Chandigarh}{Sept. 2018 - Dec. 2018}{Teaching Assistant}{}
\item{Worked as a teaching assistant in a startup ``Code57'' , a coding bootcamp for Computer Programming}
\item{Subject matter taught was mainly related to Data Structures and Algorithms}\end{rSubsection}

\begin{rSubsection}{NAV Technocrats Pvt. Ltd, Chandigarh}{Nov 2017 - Dec 2017}{Data Analyst}{}
\item{Did an analysis of Residential Properties to build an optimal prediction model for maximum profit calculation.}
\item{Increased prediction accuracy by 18\%}\end{rSubsection}

\begin{rSubsection}{National Service Scheme (NSS), PEC Branch}{May 2017 - Mar. 2018}{Volunteering Teacher}{}
\item{Taught mathematics to kids of neighbouring areas from poor households who could not afford good schooling.}
\end{rSubsection}
\end{rSection}

\begin{rSection}{Projects}
{\bf Student Identification Card Management System \hfill Dec. 2018 - April 2019}\\
Working on digitizing Student Identification Cards. Use of QR Codes based on hashed valued of IDs to securely store the shareable, ``digitally signed'' SID Card.\\ Implementation in HTML, CSS, Django and MySQL \\ \\
{\bf Analysis of Quantum Algorithms \hfill Oct 2018 - Dec 2018}\\
Worked on IBM Q5 Quantum Computer and Quirk, a classical simulator to implement Grover's Search Algorithm, Shor's Factoring Algorithm and phenomenon like Quantum Entanglement and Teleportation.\\
\\{\bf Real Time Credit Card Fraud Detection System \hfill Nov 2018}\\
Made a real time credit card fraud detection system using Long-Short Term
        Memory RNN Model. \\


\end{rSection}
%----------------------------------------------------------------------------------------
%	TECHNICAL STRENGTHS SECTION
%----------------------------------------------------------------------------------------
\pagebreak
\begin{rSection}{Technical Strengths}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Languages \ & C/C++, Python, \LaTeX, Qiskit, Bash, MySQL \\
Software \& Tools & MatLab, GNU Octave, Adobe Photoshop, Proteus, Django\\
Operating Systems & Linux (Debian), Windows 7/8/8.1/10\\
\end{tabular}

\end{rSection}

\begin{rSection}{Extra-Cirrucular} \itemsep -3pt
Gave a workshop on Amortization and it's applications in CS in association with IEEE-PEC.
\item Gave a workshop on Parallel Programming using OpenMP in association with ACM-PEC.
\item Finished fourth at Infosys Makeathon held at Infosys, Chandigarh in Oct 2018.  
\item Completed a Short Term Course in 'Mathematics in Engineering` held at PEC in June of 2018. \\ Presented on Quantum Computing in the same course.
\item Attended the National Seminar on Semiconductor Technology in May 2018
\item Passed 'A' Certificate examination of National Cadet Corps 
\item Quarter Finalist at UILS and Symcharcha intervarsity debating competitions.
\item Regular participant at various MUNs and Parliamentary Debates across North India
\item Awarded Cyber WhizKid, a school level excellence award in computers and related technology presented to one student per academic year for 2013-14.
\item Secured International Rank 46 in National Cyber Olympiad in January 2015 and 128 in February 2013.
\item Finished Third place in Intra-School Web Designing Competition in September 2014  

\end{rSection}
\begin{rSection}{Academic Interests}
 Quantum Computing and Information Science \hfill  Graph Theory\ \item Algorithmic Study \hfill Theoretical Computer Science
\end{rSection}

\begin{rSection}{Memberships}
 Student member of ACM since 2018
\item Member of IEEE Student Branch, PEC since 2017
\item Member of SAASC, the literary and debating society of PEC
\end{rSection}

\begin{rSection}{Personal Traits}
Strong verbal and written communication skills.
\item Highly focused under pressure. 
\item Like to relate everyday phenomenon with CS concepts and think of the optimal solution to problems. 
\end{rSection}
\end{document}
